Developing Address Clustering Heuristics for Account-Based Blockchain Networks: An Analysis based on a Specific Address Set

### 2023-08-25 paper.tex
Update abstract

\vspace{1em}
\onehalfspacing
\begin{center}
\section*{Abstract}
\end{center}
%Privacy, entity clustering, blockchains
This paper examines heuristics to cluster blockchain addresses using Ethereum and Polygon PoS on-chain data. We investigate the number of entities represented by over 470 thousand addresses collected from Decentraland movement data over the course of nine months. For this purpose, we assess various existing heuristics, adapt them to our specific research context, and introduce a novel heuristic. Our findings suggest that graph representation learning, particularly our variation of node embedding algorithms, to be the most effective approach for clustering a pre-defined address set. However, the method does not come without its drawbacks, which is why we discuss extension possibilities for improving clustering performance. \\

>>>>

\vspace{1em}
\onehalfspacing
\begin{center}
\section*{Abstract}
\end{center}
Given the negligible cost of creating blockchain addresses, the notion that one address equates to one user is flawed. Therefore, Blockchain Address Clustering emerges as a key tool for estimating the actual number of users. This paper examines heuristics to cluster addresses using Ethereum and Polygon PoS on-chain data, analyzing over 470,000 addresses collected from Decentraland over the course of nine months. We assess various existing heuristics, adapt them to our specific research context, and also introduce a novel heuristic. Our findings suggest that graph representation learning, particularly our variation of a node embedding algorithm, is the most effective approach for clustering a pre-defined address set. However, the method does not come without its drawbacks, which is why we propose possible extensions for improving clustering performance. \\
